Assessing the Impact of Financial Assistance on Business and Income Outcomes: A Gender-Specific Analysis

### 2024-02-15 paper/paper.qmd
revise paper

---
title: "Assessing the Impact of Financial Assistance on Business and Income Outcomes: A Gender-Specific Analysis"
author: "Dingning Li, Yiming Tang, Yingqi Pang"
abstract: "This study replicates and extends previous research on the differential impacts of financial support on microenterprise performance, with a focus on the entrepreneurs' gender. By analyzing data from 3,294 entrepreneurs, we explored the effects of loans, cash grants, and in-kind grants on business ownership, assets, and profitability, while taking personal characteristics into account. Our findings suggest that all forms of financial assistance positively influence microenterprise growth, with in-kind grants being particularly advantageous, especially for female entrepreneurs. This research underscores the importance of tailoring financial interventions to consider gender differences, aiming to promote economic empowerment and enhance microenterprise resilience."
date: "`r format(Sys.time(), '%d %B %Y')`"
format: pdf
---

# Introduction

@@

We replicate the paper by Bruno Crépon, Mohamed El Komi, and Adam Osman, focusing on the research question: Does the type of financial support have an impact on the overall performance of enterprises, and is this impact related to the gender of the entrepreneur? The three treatments are microcredit, in-kind grants, and cash grants. Our estimands quantify the expected impact of the type of financial support on our main variables:
- **Business Ownership**: Estimating the effect of financial support on the probability of owning a business post-intervention.
- **Monthly Expenses**: Assessing how different types of financial support influence the monthly expenses of businesses.
- **Monthly Profits**: Determining the role of financial support in enhancing business profitability.
- **Monthly Revenue**: Evaluating the impact of financial support on business sales activity.
- **New Assets**: Measuring the ability of financial support to enable businesses to acquire new assets post-intervention.
- **Labour Income**: Summing monthly profits, wages, and other labour income, providing a comprehensive view of the entrepreneur's earnings.
- **Total Income**: A broader measure of income that includes profits, rent, other incomes, government support, and transfers, offering a complete picture of the financial benefits of the intervention.

In this study, we will describe our experimental design and data collection methods in Data section, detailing the allocation of financial support types and the systematic tracking of growth indicators for microenterprises. Experiment section will provide an analytical narrative of our findings, showcasing the impact of microcredit, cash grants, and in-kind grants on the sustainability and expansion of businesses. We then delve into the gender-based differences in outcomes in Discussion section, uncovering significant insights into the variable effects of financial interventions. The concluding section will offer practical policy recommendations and propose directions for future research, underscoring the crucial role of customized financial strategies in supporting the success of microenterprises.

The original research paper used Stata for data processing and analysis within its replication package. However, we opted for R [@citeR] to conduct all data organization and analysis. We used a suite of R libraries including `haven` [@haven] for reading Stata files, `readr` [@citereadr] for data import, `ggplot2` [@citeggplot2] for data visualization, `dplyr` [@citedplyr] for data manipulation, `knitr` [@citeknitr] for report generation, `kableExtra` [@citekableExtra] for table formatting, and `stargazer` [@stargazer] for creating regression tables. These libraries were selected for their functionality and compatibility with our dataset and analysis requirements.

# Experiment 
// TODO: Table 1: Baseline Balance of Variables Across Treatment Status
This experiment appears to have been designed to assess the influence of four treatments on a range of business-related outcomes. The process of randomization was employed to ensure that each participant in the experiment had an equal chance being assigned to any treatment groups. This methodological choice that facilitates the balancing of known and unknown mixing variables in these groups. Table 1 provided suggest that this randomization process was successful, as indicated by the balance check labeled “TRUE”. It confirms that the baseline characteristics were evenly distributed among the different treatment groups. This implies that any subsequent differences can be attributed to the effects of the treatments confidently rather than pre-existing differences among participants.

::: {.figure}
![Baseline Balance](../outputs/tables/baseline_balance.png){width=99%}
:::

# Data Cleaning and Processing

@@

We began by loading the dataset from two Stata files using the `haven` package. The pre-intervention (`pre_data`) and post-intervention (`out_data`) data were both read and filtered to include only the entries that were present in both datasets, ensuring consistency and completeness for each subject across the study timeline.
A new dataset (`new_data`) was created to store the cleaned variables. We treated the `treatment_status` variable by creating dummy variables for each type of financial support, which were then bound to `new_data`. 
We defined several key outcome variables to assess the impact of the financial interventions:

@@

We assessed the impact of financial interventions using several outcome variables:
- **Business Ownership (`hasbiz`)**: A binary outcome variable indicating whether an entrepreneur owned a business. An individual does not have business if they do not have project or have no income source.
- **New Business Assets (`new_biz_assets`)**: A continuous variable representing the total value of new assets acquired by the business post-intervention. It is defined by the sum of inventory stocks, finished goods, liquid cash reserves, value of new business premises, recently purchased land, furniture, machinery and equipment, vehicles, and the cost of maintenance for these assets. 
- **Monthly Expenses**: A continuous variable summing all monthly costs incurred by the business. This reflects the immediate financial activity and potential expansion resulting from the intervention.
- **Monthly Profits (`monthly_profits`)**: Calculated as the difference between revenue and expenses, this variable measures the profitability of the business, a key indicator of financial viability.
- **Monthly Revenue (`monthly_revenue`)**: The total monthly sales before costs, representing the operational turnover and market activity of the business.

## Income Variables

We also computed income-related variables that aggregate various income sources:
- **Labour Income (`labour_inc`)**: It is calculated by summing the monthly profit, wage income, and other labour income source.
- **Total Income (`total_inc`)**: It is calculated by summing the monthly profit, wages, rental income from assets, other income streams not categorized as labor income, government support values, and received transfers.

@@

@@

After cleaning, we performed regression analyses to understand the impact of financial interventions on business outcomes and income. The `lm` function in R was used to estimate the effects of microcredit, in-kind grants, and cash grants on various business and income outcomes. Custom functions were defined to streamline the regression analysis and visualization of results. 
The `regress` function was employed to carry out linear regressions for the treatment effects on specified outcome variables. Regression plots were saved as JPEG files, and regression tables were created in HTML format using the `stargazer` package.

To ensure that our treatment groups were comparable at baseline, we conducted a balance check. This involved regressing the treatment status on a set of pre-treatment covariates to confirm that the randomization process was successful.

@@

# Results

@@

// TODO: Impacts fof Financial Supports on Business Outcomes

Table 2 provides a comprehensive summary of the business outcome for participants across different financial support programs: Micro Credit, In-Kind Grant, and Cash Grant. The table illustrates key financial indicators such as business ownership, acquisition of new assets, monthly expenditure, monthly revenue and monthly profit. Each entry is accompanied by standard errors in parentheses, offering insights into the variability and reliability of the observed data. The number of observations, denoted by N, stands at 3075 in total for each category, which indicates sample size for the analysis. The table summarize varied impacts of the different financial interventions on the economic activities of the participants. In the following discussion, we will examine the empirical data presented in Table1 for analyzing the effectiveness of these financial support mechanisms in contributing to the business outcomes.

::: {.figure}
![Business Outcome](../outputs/tables/business_outcome.png){width=99%}
:::

@@

@@

//TODO: Table 3.1:  Impacts of Financial Supports on Business Outcomes Among Female Participants

The table summarizes the business outcome for female participation, illustrating a detailed impact of financial interventions, there is a marginal positive effect on the likelihood of having a business with Micro credit and In-kind Grant, while Cash Grant shows a slight negative influence. When looking at the acquisition of new assets, all these three financial supports are associated with significant negative impacts. Monthly expenditures also decreased across all types of financial aid, suggesting a reduction in business spending. Monthly profit shows a relatively small negative influence compared with New Asset for all financial assistance. Notably, only Monthly profit depict a positive change with the receipt of an In-Kind Grant, Micro Credit and Cash Grant, these effects are relatively small and less likely observed with other forms of capital assistance. This pattern highlights the complex relationship between the type of financial support and varied business outcomes among female leaders.

::: {.figure}
![](../outputs/tables/business_outcome_female.png){width=99%}
:::

//TODO: Table 3.2: Impacts of Financial Supports on Business Outcomes Among Male Participants
For the male participants in our study, the impact of various form of capital assistance displays the same complex pattern across different business outcomes. The likelihood of owning a business does not significantly change with the introduction of Micro Credit, In-Kind Grant, or Cash Grant, it’s evident by the negligible coefficients. However, positive performances are shown on the New Asset, with the latter showing a slightly larger effect on In-Kind Grant. Monthly Expenditure decreases significantly with all forms of capital assistance, which may indicate more efficient business operations or a reduction in business size or activity, which is similar with that of female participants. In terms of Monthly Revenue, we observed a decline with Micro Credit and a more obvious decline with Cash Grants, but there is only slight change with In-Kind Grants. Lastly, Monthly Profit does not show notable improvement with the capital assistance provided, although there is a insignificant trend towards reduced profits, particularly with Micro Credit and Cash Grants.

::: {.figure}
![](../outputs/tables/business_outcome_male.png){width=99%}
:::

@@

::: {.figure}
![Female Monthly Profit](../outputs/figures/femaleFemale - Monthly Profit.jpg){width=49%}
![Male Monthly Profit](../outputs/figures/maleMale - Monthly Profit.jpg){width=49%}
:::

@@

::: {.figure}
![Female Monthly Profit](../outputs/figures/femaleFemale - New Asset.jpg){width=49%}
![Male Monthly Profit](../outputs/figures/maleMale - New Asset.jpg){width=49%}
:::

@@

//TODO: Table 4.1: Impacts of Financial Supports on Income Outcomes Among Female Participants
```{=latex}
\input{../outputs/tables/income_outcome_female.tex}
```

//TODO: Table 4.2: Impacts of Financial Supports on Income Outcomes Among Male Participants
```{=latex}
\input{../outputs/tables/income_outcome_male.tex}
```

Before we study the differential impact of financial support on Business Outcomes across genders, Income Outcomes is also a crucial for researching effective economic empowerment programs. Table 4.1 and Table 4.2 offers insight into gender-specific outcomes of three financial supports on income. The data can be analyzed to compare the influence affecting labor income and total income for female and male participants. For female participants, Both Cash Grant and In-Kind Grant appear to have the significant positive effect on both labor and total income, with more substantial effect by providing Cash Grant. Micro Credit, while showing a positive in labor income but converse effect on total income. On the male side, the effects of financial supports are less clear, with Micro Credit and In-Kind Grant associated with decrease in labor income and no clear pattern in total income. However, Cash Grant show a slight positive effect on labor income but a decrease in total income. 
If we compare the gender-specific effect, it seems that women benefit more from financial supports in terms of income outcomes. This aligns with the idea that women may perform between than men with these types of financial support when it comes to income outcomes.

@@

## What is the meaning of our research?"

>>>>

---
title: "Assessing the Impact of Financial Assistance on Business and Income Outcomes: A Gender-Specific Analysis"
author: "Dingning Li, Yiming Tang, Yingqi Pang"
abstract: "This study replicates and extends previous research on the differential impacts of financial support on microenterprise performance, with a focus on the entrepreneurs' gender. By analyzing data from 3,294 entrepreneurs, we explored the effects of loans, cash grants, and in-kind grants on business ownership, assets, and profitability, while taking personal characteristics into account. Our findings suggest that all forms of financial assistance positively influence microenterprise growth, with in-kind grants being particularly advantageous, especially for female entrepreneurs. This research underscores the importance of tailoring financial interventions to consider gender differences, aiming to promote economic empowerment and enhance microenterprise resilience."
date: February 10, 2024
date-format: long
format: pdf
bibliography: references.bib
toc: true
toc-depth: 3
---
# Introduction

@@

We replicate the paper by Bruno Crépon, Mohamed El Komi, and Adam Osman, focusing on the research question: **Does the type of financial support have an impact on the overall performance of enterprises, and is this impact related to the gender of the entrepreneur?** There are three financial assistance treatments: **microcredit**, **in-kind grants**, and **and cash grants**.

We aim to estimate the average treatment effect of the different type of financial assistance on the main business performance estimants, including four business outcome estimands: **Business Ownership**, **Monthly Expenses**, **Monthly Profits**, **Monthly Revenue**, and **New Assets**, and two income outcome estimands: **Labour Income**, 
**Total Income**. The detailed explanation of each variables are shown in the data section.

In this paper, we will first describe our experimental design, data cleaning procedure, and main variables introduction, detailing the allocation of financial support types and the systematic tracking of growth indicators for microenterprises. Model & Results section will briefly introduce our model architecutre to estimate the average treatment effect and provide an analytical narrative of our findings, showcasing the impact of microcredit, cash grants, and in-kind grants on the sustainability and expansion of businesses. We then delve into the gender-based differences in outcomes in Discussion section, uncovering significant insights into the variable effects of financial interventions. The discussion section will offer practical policy recommendations and propose directions for future research, underscoring the crucial role of customized financial strategies in supporting the success of microenterprises.

In terms of the statistical package being used, the original research paper used Stata for data processing and analysis within its replication package. However, we opted for R [@citeR] to conduct all data organization and analysis. We used a suite of R libraries including `haven` [@haven] for reading Stata files, `readr` [@citereadr] for data import, `ggplot2` [@citeggplot2] for data visualization, `dplyr` [@citedplyr] for data manipulation, `knitr` [@citeknitr] for report generation, `kableExtra` [@citekableExtra] for table formatting, and `stargazer` [@stargazer] for creating regression tables. These libraries were selected for their functionality and compatibility with our dataset and analysis requirements.

# Data

@@

We began by loading the dataset from two Stata files using the `haven` package. The pre-intervention (`pre_data`) and post-intervention (`out_data`) data were both read and filtered to include only the entries that were present in both datasets, ensuring consistency and completeness for each subject across the study timeline.
A new dataset (`new_data`) was created to store the cleaned variables.

## Treatment Variables
We treated the `treatment_status` variable by creating dummy variables for each type of financial support, resulting in four different treatment levels:
- **Control ()**: 
- **Other()**
# TODO: ADD variable name and explanation for four different treatment dummies

...

We defined several key outcome variables to assess the impact of the financial interventions:

@@

We assessed the impact of financial interventions on several outcome variables:

- **Business Ownership (`hasbiz`)**: A binary outcome variable indicating whether an entrepreneur owned a business. An individual does not have business if they do not have project or have no income source.
- **New Business Assets (`new_biz_assets`)**: A continuous variable representing the total value of new assets acquired by the business post-intervention. It is defined by the sum of inventory stocks, finished goods, liquid cash reserves, value of new business premises, recently purchased land, furniture, machinery and equipment, vehicles, and the cost of maintenance for these assets. 
- **Monthly Expenses**: A continuous variable summing all monthly costs incurred by the business. This reflects the immediate financial activity and potential expansion resulting from the intervention.
- **Monthly Profits (`monthly_profits`)**: Calculated as the difference between revenue and expenses, this variable measures the profitability of the business, a key indicator of financial viability.
- **Monthly Revenue (`monthly_revenue`)**: The total monthly sales before costs, representing the operational turnover and market activity of the business.
- **Labour Income (`labour_inc`)**: It is calculated by summing the monthly profit, wage income, and other labour income source.
- **Total Income (`total_inc`)**: It is calculated by summing the monthly profit, wages, rental income from assets, other income streams not categorized as labor income, government support values, and received transfers.

@@

## Control Variables

@@

@@

# Experiment

In original paper, the experiment have been designed to assess the causal effect of the financial intervention treatments on main business outcome. The process of randomization was employed to ensure that each participant in the experiment had an equal chance being assigned to any treatment groups. This methodological choice that facilitates the balancing of known and unknown mixing variables in these groups.

To verify the randomization process, we conducted a balance check on various control variable. This involved regressing the treatment status on a set of pre-treatment covariates to confirm that the randomization process was successful. Table 1 provided suggest that this randomization process was successful, as indicated by the fact that there is no significant covariate difference among each treatment group. It confirms that the baseline characteristics were evenly distributed among the different treatment groups. This implies that any subsequent differences can be attributed to the effects of the treatments confidently rather than pre-existing differences among participants.

```{=latex}
\input{../outputs/tables/baseline_balance.tex}
```

# Model & Results

## Model Architecture

We model financial interventions' effects on business outcomes as:
$$
Y_i = \alpha + \sum_{T \in \{L, IK, C\}} \beta_{T} \text{Treatment}_{iT} + \gamma X_i + u_i
$$
where $Y_i$ is business performance, $\beta_{T}$ treatment effects, $\gamma X_i$ observed covariates, and $u_i$ unobserved factors.

For gender differences, the model expands to:
$$
Y_i = \alpha + \sum_{T \in \{LF, IKF, CF, LM, IKM, CM\}} \beta_{T} \text{Treatment}_{iT} + \theta \text{Gender}_i + \gamma X_i + \delta \text{cohort} + u_i
$$
$\theta$ signifies gender effects.

Analysis uses R's `lm` function, with `stargazer` for LaTeX-formatted tables.

@@

Table 2 provides a comprehensive summary of the business outcome for participants across different financial support programs: Micro Credit, In-Kind Grant, and Cash Grant. The table illustrates key financial indicators such as business ownership, acquisition of new assets, monthly expenditure, monthly revenue and monthly profit. Each entry is accompanied by standard errors in parentheses, offering insights into the variability and reliability of the observed data. The number of observations, denoted by N, stands at 3075 in total for each category, which indicates sample size for the analysis. The table summarize varied impacts of the different financial interventions on the economic activities of the participants. In the following discussion, we will examine the empirical data presented in Table 2 for analyzing the effectiveness of these financial support mechanisms in contributing to the business outcomes.

@@

```{=latex}
\input{../outputs/tables/business_outcome.tex}
```

@@

Table 3 summarizes the business outcome for female participation, illustrating a detailed impact of financial interventions, there is a marginal positive effect on the likelihood of having a business with Micro credit and In-kind Grant, while Cash Grant shows a slight negative influence. When looking at the acquisition of new assets, all these three financial supports are associated with significant negative impacts. Monthly expenditures also decreased across all types of financial aid, suggesting a reduction in business spending. Monthly profit shows a relatively small negative influence compared with New Asset for all financial assistance. Notably, only Monthly profit depict a positive change with the receipt of an In-Kind Grant, Micro Credit and Cash Grant, these effects are relatively small and less likely observed with other forms of capital assistance. This pattern highlights the complex relationship between the type of financial support and varied business outcomes among female leaders.

```{=latex}
\input{../outputs/tables/business_outcome_female.tex}
```

For the male participants in our study, as shown in Table 4, the impact of various form of capital assistance displays the same complex pattern across different business outcomes. The likelihood of owning a business does not significantly change with the introduction of Micro Credit, In-Kind Grant, or Cash Grant, it’s evident by the negligible coefficients. However, positive performances are shown on the New Asset, with the latter showing a slightly larger effect on In-Kind Grant. Monthly Expenditure decreases significantly with all forms of capital assistance, which may indicate more efficient business operations or a reduction in business size or activity, which is similar with that of female participants. In terms of Monthly Revenue, we observed a decline with Micro Credit and a more obvious decline with Cash Grants, but there is only slight change with In-Kind Grants. Lastly, Monthly Profit does not show notable improvement with the capital assistance provided, although there is a insignificant trend towards reduced profits, particularly with Micro Credit and Cash Grants.

```{=latex}
\input{../outputs/tables/business_outcome_male.tex}
```

@@

::: {.figure}
![Female Monthly Profit](../outputs/figures/femaleFemale - Monthly Profit.jpg){width=49%}
![Male Monthly Profit](../outputs/figures/maleMale - Monthly Profit.jpg){width=49%}
*Figure 1: ATT on Monthly Profit by Gender*
:::

@@

::: {.figure}
![Female Monthly Profit](../outputs/figures/femaleFemale - New Asset.jpg){width=49%}
![Male Monthly Profit](../outputs/figures/maleMale - New Asset.jpg){width=49%}
*Figure 2: ATT on New Asset by Gender*
:::

@@

Before we study the differential impact of financial support on Business Outcomes across genders, Income Outcomes is also a crucial for researching effective economic empowerment programs. Table 5 and Table 6 offers insight into gender-specific outcomes of three financial supports on income. The data can be analyzed to compare the influence affecting labor income and total income for female and male participants. For female participants, Both Cash Grant and In-Kind Grant appear to have the significant positive effect on both labor and total income, with more substantial effect by providing Cash Grant. Micro Credit, while showing a positive in labor income but converse effect on total income. On the male side, the effects of financial supports are less clear, with Micro Credit and In-Kind Grant associated with decrease in labor income and no clear pattern in total income. However, Cash Grant show a slight positive effect on labor income but a decrease in total income. 
If we compare the gender-specific effect, it seems that women benefit more from financial supports in terms of income outcomes. This aligns with the idea that women may perform between than men with these types of financial support when it comes to income outcomes.

```{=latex}
\input{../outputs/tables/income_outcome_female.tex}
```

```{=latex}
\input{../outputs/tables/income_outcome_male.tex}
```

@@

## Main Contribution
